The Tracing package\\ \large a more in depth explanation

### 2015-05-18 manual/projectrapport.tex
* minimal changes to the report/manual - -> updated information for tracers/logger/dynamic structured DEVS
Signed-off-by: Lttlemoi <lttlemoi+git@gmail.com>

Only the removal/addition of connections is currently supported. Unlike the PyPDEVS, we will try to keep a removed model intact when it is removed from the simulation.

@@

	\item crash safety. The logger will catch the following signals and flush all remaining output before exiting the program:

@@

\section{Logger}
We have also conducted a small benchmark to compare the raw power of our logger and the proposed g3log.
We let each logger print several hundred thousand messages to a file. These are the performance statistics:
\subsubsection{g3log}
\lstinputlisting[]{g3log.perf}
\subsubsection{Our own logger}
\lstinputlisting[]{own.perf}
\subsubsection{Conclusion}
While the difference is considerable, we should keep in mind that g3log generates timestamps for each message. It also contains several features that our logger doesn't, such as crash safety. Moreover, g3log allows the user to dynamically change which log levels are filtered, while this can only be decided at compile time for our logger. This can be clearly seen in the amount of branches.

>>>>

Dynamic structured DEVS is completely supported in single core simulation. This includes allowing the following structural changes during the simulation:
	\item adding/removing connections
	\item adding/removing ports
	\item adding/removing submodels.
These changes are only allowed during a special phase of the simulation. The simulator provides a map object of type \lstinline[language=C++,basicstyle=\small\color{black}]{std::multimap<std::string, std::string>} that can be used for communication and cooperation between the models. During one simulation step, this communication always happens from bottom to top. Only models that had an internal transition are considered for performing dynamic structured.\\
Unlike the PyPDEVS, we will try to keep a removed model intact when it is removed from the simulation.

@@

	\item basic crash safety. The logger will catch the following signals and flush all remaining output before exiting the program:

@@

\section{Logger}
We have also conducted a small benchmark to compare the raw power of our logger and the proposed g3log.
We let each logger print several hundred thousand messages to a file. These are the performance statistics:
\subsubsection{g3log}
\lstinputlisting[]{g3log.perf}
\subsubsection{Our own logger}
\lstinputlisting[]{own.perf}
\subsubsection{Conclusion}
While the difference is considerable, we should keep in mind that g3log generates timestamps for each message. It also contains several features that our logger doesn't, such as extensive crash safety. Moreover, g3log allows the user to dynamically change which log levels are filtered, while this can only be decided at compile time for our logger. This can be clearly seen in the amount of branches.

### 2015-05-18 manual/tracersReport.tex
* minimal changes to the report/manual - -> updated information for tracers/logger/dynamic structured DEVS
Signed-off-by: Lttlemoi <lttlemoi+git@gmail.com>

\part*{Individual tracer}
A Tracer has to generate output for certain events and send it to some output sink.\\
Each individual tracer class has the exact same structure. Policy-based programming\footnote{Policy-based programming: \href{http://en.wikipedia.org/wiki/Policy-based_design}{Wikipedia}} is used to separate the output writing logic from the output creation logic. This allows the user to use their own output method without having to rewrite all the existing tracers.\\
\subsection{Policies}
An output policy dictates where the generated output will go to. At the moment, we have implemented a policy for writing the output to \inlinecpp{std::cout} and another policy for writing the output to a file.
\section{Planned changes}
At the moment, we have only implemented one tracer, the verbose tracer. The other tracers (XML, JSON and CELL) will have a very similar structure. We could just create a single base class and use virtual functions to provide the implementation of the tracer-specific functionality. However, this would defeat the purpose of custom designing the template classes we have already. Another option is to use the Curiously Recurring Template Pattern (CRTP)\footnote{CRTP: \href{http://en.wikipedia.org/wiki/Curiously_recurring_template_pattern}{Wikipedia}}.
\paragraph{Curiously Recurring Template Pattern} This pattern allows a base class to call functionality of a derived class without having to use virtual functions or function overloading. It is in effect a way to deal with this kind of polymorphic behavior at compile time. The compiler knows exactly which functions will be called by the base class and can therefore use optimization techniques that are not always available when using runtime polymorphism.

>>>>

\part*{Individual tracers}
A Tracer has to generate output for certain events and send it to some output sink.\\
Each individual tracer class has the exact same structure. Policy-based programming\footnote{Policy-based programming: \href{http://en.wikipedia.org/wiki/Policy-based_design}{Wikipedia}} is used to separate the output writing logic from the output creation logic. This allows the user to use their own output method without having to rewrite all the existing tracers.\\
\section{Policies}
An output policy dictates where the generated output will go to. At the moment, we have implemented a policy for writing the output to \inlinecpp{std::cout}, a policy for writing the output to a file and a policy that will write to multiple files.
\paragraph{note:} Only the CELL tracer will make proper use of the multi-file output policy. The other policies can be used by all tracers.
\section{Tracers}
At the moment, we have implemented the following tracers:
\begin{itemize}
	\item Verbose
	\item XML
	\item JSON
	\item CELL
\end{itemize}
Because the \emph{Verbose}, \emph{XML} and \emph{JSON} tracers have a very similar structure and share a large portion of code, we created a single base class. The Curiously Recurring Template Pattern (CRTP)\footnote{CRTP: \href{http://en.wikipedia.org/wiki/Curiously_recurring_template_pattern}{Wikipedia}} is used for the tracer-specific details.
\paragraph{Curiously Recurring Template Pattern} This pattern allows a base class to call functionality of a derived class without having to use virtual functions or function overloading. It is in effect a way to deal with this kind of polymorphic behavior at compile time. The compiler knows exactly which functions will be called by the base class and can therefore use optimization techniques that are not always available when using runtime polymorphism.
